---
title: "drake_specification"
author: "Lukas Huber"
date: "2020-7-31, last update (`r Sys.Date()`)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{drake_specification}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This template demonstrates traceability of a drake plan as a sequence of execution steps.

First the `setup` chunk sets the path to the project root - to conviently work with reproducible file-paths in headless and rstudio modes.

```{r setup}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

This code sources the current projects files - packages required, functions required and the base drake plans.

```{r}
pkgload::load_all()
#source("R/packages.R")
#source("R/functions.R")
#source("R/plan.R")
```

The first line of the following chunk forces a re-run of the whole drake workflow - comment it to see, if drake validates the current step.

```{r}
drake::clean()
drake::make(scenario_wrapper())
```

```{r}
vis_drake_graph(scenario_wrapper())
```

## Mandrake - limited

Mandrake allows us to annotate and advance the documentation of a drake graph.

```{r eval=F}
```


```{r eval=F}
lookup_cache <- mandrake::load_package_colspec("reproducibleFairTemplate")
```

```{r eval=F}
cache <- drake::drake_cache()
plan_extracted <- scenario_wrapper() %>%
  mandrake::decorate_plan(cache=cache, 
                          lookup_cache = lookup_cache,
                          desc_colname = "desc")
```

```{r eval=F}
my_config <- drake_config(plan_extracted)
graph_info <- drake_graph_info(
  my_config, 
  group = "cluster_id", 
  clusters = c("summ", "coef"), 
  build_times = "none",
  on_select_col = "desc")

graph <- render_drake_graph(
  graph_info,
  on_select = "embedHandler",
  ncol_legend = 4) %>% 
  mandrake::attach_dependencies()
```

```{r eval=F}
graph
```





## Buidling of the analytic package

This section considers the build steps involved in the development and extension of an analysis.

First - be sure to document your package using roxygen with the following chunk.

```{r}
#devtools::document()
```

```{r}
#renv::snapshot()
```

## Version_control

In order to look into the git commit history from R - one can use the gert library to see what happened.

```{r eval=F}
library(gert)
```
```{r eval=F}
git_log()
```
```{r eval=F}
git_status()
```

