---
title: "Getting Started"
author: "Lukas Huber"
output: html_notebook
---


## Introduction

There are two main ways to use this template:

- As a project starter. For this, use Git clone and change the remote to your repository. This starts a clean, fresh project.
- As a reference. In that case, you use the project template and parts as reference.

In both cases, no one must utilize all provided packages and patterns, one can gradually improve reproducibility.






## Prerequisites



## Getting Started


In order to start with your reproducible Project use the following steps to get the template running:

- Your Project should use Git.

- Your Project MUST have a README file

- Define a license for your Project.

- Utilize an environment tool (renv)

- Turn your project into a package structure

- Lint your code to follow good styleguides.

- Decide where to host your data

- Use version control for everything

- Publish your work with a repository.

- Use continous integration

- Use code tests

- Use software engineering practices like docstrings, roxytest, 

- use workflows like drake, targets

- utilize PROV-Tools (rdtlite)

- package your results (rocrate)


Then you need to consider a few questions on how you want to start building your package:

- Hypotheses you need to investigate
- Long-term traceability
- Base data quality
- ETL-Process
- Analytic processes


### Scenario 1: walk-through

The scenario 1 is one simple scenario involving several steps in a linear manner.

The file is in `vignettes/scenario_1.Rmd`, it utilizes `R/packages.R"` for package loading, `R/functions.R` for general functions,
`R/functions_scenario_1.R` for scenario specific functions and the plan is defined in `R/plan.R`

### Test-Results

```{r}
testthat::test_local("../")
```

### Complete Provenance

```{r eval=F}
rdtLite::prov.run("../R/make.R", prov.dir="../.prov/")
```


### Provenance Curation

```{r eval=F}
drake::clean() #clean the cache to force rebuild
drake::clean(destroy=TRUE) # clean cache and curate "one" clean run in the drake cache.
```


### Development Steps

Description of steps during development, starting with Docker + RStudio right away.

1. clone this template

```
git clone https://github.com/g4challenge/repro-fair-neuro-ds-template
```

2. within the git repository, start the docker container:

```
docker run --rm -p 8787:8787 -e PASSWORD="1234" -v $(pwd):/home/rstudio my_fair_project 
```

3. open your browser at http://localhost:8787 

4. login using user=`rstudio` password=`1234`

5. click open on the .rproj file.

6. Start using the project, adapt it to your needs + change the git remote


- Local Docker build
    
    docker build . -t my_fair_project

- Local Docker run with default user `rstudio` and PASSWORD="1234" - use different password

```
docker run --rm -p 8787:8787 -e PASSWORD="1234" -v $(pwd):/home/rstudio g4challenge/repro-fair-neuro-ds-template
```

## (Next) Steps

Getting Started
Description of the next analysis steps. How to use this package:

1. start by cloning/forking the git repository
2. use git+github, git lfs, tidyverse and RMarkdown
3. add Drake Plans to for your Pipeline(s)
4. (optional) start the RStudio IDE within Docker + use renv


### FAQ

Where should I start my documentation? 


How do the various documentations relate to each other? 


What adaptations do I have to make? 

How can a prioritize these adaptations? 

What is the minimal set of adaptations that I need to make? 


Can I also apply this to other contexts within medicine, or even outside of a medical context or?
