---
title: "Scenario 1"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{scenario_1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This notebook handles the rendering of scenario_1 - which is a simple case of a hypotheses - import dataset - transform dataset - generate report and evaluate the process and result.

```{r setup}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

# Question

The simulated hypotheses is to generate a CPP(cerebral perfusion pressure) based on raw_data. The following chunk instantiates packages, functions and plans.

```{r}
pkgload::load_all()
```

In order to avoid errors in reproduction of R package runs - the drake cache is cleaned.

```{r eval=T}
drake::clean()
# check file existing
#file.exists("data/raw_data.xlsx")
```

The `scenario_wrapper`-function returns the instantiated scenario plan as drake "tibble".

```{r}
drake::make(scenario_wrapper())
```

```{r}
drake_history()
```

```{r}
vis_drake_graph(scenario_wrapper())
```

